Hydra Battles and Cie

### 2020-12-10 doc/chapter-powers.tex
minor corrections

Lemma FFK_correct :
  forall (p q  : positive) (fp fq : Fchain),
    Fchain_correct p fp  ->
    Fchain_correct q fq ->
    Fchain_proper fp ->
    Fchain_proper fq -> Kchain_correct  (p * q ) p (FFK fp fq).
(* Proof omitted *)

Instance FFK_proper 
   (fp: Fchain) (fq : Fchain)
    (_ :   Fchain_proper fp)
    (_ :  Fchain_proper fq) :  Kchain_proper (FFK fp fq) .
(* Proof omitted *)
\end{Coqsrc}

>>>>

Lemma FFK_correct  (p q  : positive) (fp fq : Fchain):
    Fchain_correct p fp  ->
    Fchain_correct q fq ->
    Fchain_proper fp ->
    Fchain_proper fq -> Kchain_correct  (p * q ) p (FFK fp fq).
(* Proof omitted *)

Instance FFK_proper  (fp fq : Fchain)
    (_ :   Fchain_proper fp)
    (_ :  Fchain_proper fq) :  Kchain_proper (FFK fp fq) .
(* Proof omitted *)
\end{Coqsrc}

### 2020-12-10 doc/hydras.tex
Added traces of addition chains Small modification of the documentation
minor corrections

@@

\cleardoublepage

% \mbox{~}
% \clearpage
% \newpage
% \mbox{~}
\vspace{10cm}
\begin{quote} 
{ \Large {\it
``I start from one point and go as far as possible.'' }

John Coltrane.}
\end{quote}

@@

Among all the theorems proved with the help of proof assistants like \coq{}, \isabelle{}~\cite{isabelle}, \hol{}~\cite{HOL}, etc.,
several statements and proofs  share some interesting features:
\begin{itemize}
\item Their statements are easy to understand, even by non-mathematicians
\item Their proof requires some non-trivial mathematical tools
\item Their mechanization on computer presents some methodological interest.
\end{itemize}

@@

Any form of contribution  is welcome: correction of errors (typos and more serious mistakes), improvement of
Coq scripts, proposition of inclusion of new chapters, and generally any
comment or proposition that would help us. The text contains several \emph{projects} which, when completed, may improve the present work.
Please do not hesitate to bring your contribution!

@@

  \begin{Coqsrc}
 Require Import Arith.

 Definition square (n:nat) := n * n.

@@

\begin{Coqbad}
Require Import Lia.

Module Bad.

@@

\begin{Coqalt}
Require Import Arith Lia Iterates.
Module Alt.
  Definition double (n : nat) := iterate S n n.
End Alt.
\end{Coqalt}

@@

\section{Acknowledgements}
\label{sec:orgheadline5}
    Many thanks to Yves Bertot, David Ilcinkas, Karl Palmskog, Sylvain Salvati, Alan Schmitt and Théo Zimmerman for their help on the elaboration of this document, and to the
 members of the \emph{Formal Methods} team at laBRI for their helpful comments 
on an oral presentation of this work.

>>>>

%\SetWatermarkLightness{0.8}
\definecolor{lightorange}{rgb}{1,0.7,0.5}
\SetWatermarkScale{0.35}
\SetWatermarkText{Work in Progress}
\SetWatermarkColor{lightorange}

@@

% \cleardoublepage

% % \mbox{~}
% % \clearpage
% % \newpage
% % \mbox{~}
% \vspace{10cm}
% \begin{quote} 
% { \Large {\it
% ``I start from one point and go as far as possible.'' }

% John Coltrane.}
% \end{quote}

@@

Among all the theorems proved with the help of proof assistants like \coq{}~\cite{Coq,BC04}, \hol{}~\cite{HOL}, \isabelle{}~\cite{isabelle},  etc.,
several statements and proofs  share some interesting features:
\begin{itemize}
\item Their statements are easy to understand, even by non-mathematicians
\item Their proof requires some non-trivial mathematical tools
\item Their mechanization on computer presents some methodological interest.
\end{itemize}

@@

Any form of contribution  is welcome: correction of errors (typos and more serious mistakes), improvement of
Coq scripts, proposition of inclusion of new chapters, and generally any
comment or proposition that would help us. The text contains several \emph{projects} which, when completed, may improve the present work.
Please do not hesitate to bring your contribution, for instance with Github's proof requests and issues. Thank you in advance!

@@

  \begin{Coqsrc}
 Definition square (n:nat) := n * n.

@@

\begin{Coqbad}
Module Bad.

@@

\begin{Coqalt}
From hydras Require Import Iterates.
Module Alt.
  Definition double (n : nat) := iterate S n n.
End Alt.
\end{Coqalt}

@@

\section{Acknowledgements}
\label{sec:orgheadline5}
    Many thanks to Yves Bertot, David Ilcinkas, Karl Palmskog, Sylvain Salvati, Alan Schmitt and Théo Zimmerman for their help on the elaboration of this document, and to the
 members of the \emph{Formal Methods} team at laBRI for their helpful comments 
on  oral presentations of this work.

### 2020-12-10 doc/part-hydras.tex
minor corrections

In order to describe trees where each node can have an arbitrary (but finite) number of sons, it usual to define a type where each node carries a \emph{forest}, \emph{i.e} a list of trees
(see for instance Chapter 14, pages 400-406 of \cite{BC04}).

@@

\vspace{4pt}
\emph{From Module~\href{../theories/html/hydras.Hydra.Hydra_Definitions.html\#Hydra}{Hydra.Hydra\_Definitions}}

@@

\emph{From Module~\href{../theories/html/hydras.Hydra.Hydra_Definitions.html\#head}{Hydra.Hydra\_Definitions}}

@@

\vspace{4mm}
\emph{From Module~\href{../theories/html/hydras.Hydra.Hydra_Examples.html\#Hy}{Hydra.Hydra\_Examples}}

@@

\emph{From Module~\href{../theories/html/hydras.Hydra.Hydra_Definitions.html\#hcons_mult}{Hydra.Hydra\_Definitions}}

@@

(** hydra with n copies of the same daughter *)

@@

\emph{From Module~\href{../theories/html/hydras.Hydra.Hydra_Examples.html}{Hydra.Hydra\_Examples}}

@@

When defining a recursive function over the type \texttt{Hydra}, one has to consider the three constructors 
\texttt{node}, \texttt{hnil} and \texttt{hcons} of the mutually inductive types \texttt{Hydra} and \texttt{Hydrae}. 
Let us define for instance the function which  computes the number of nodes of any hydra:

@@

Let us now use \texttt{Hydra\_rect2} for proving that the height of any hydra is strictly less than its size.
Using this scheme requires an auxiliary predicate, called \texttt{P0} in \texttt{Hydra\_rect2}'s statement. 
Let us begin by defining an ad-hoc version of \texttt{List.Forall}.

@@

The rest of the definition is structured as two mutually inductive relations on hydras and sequences of hydras. The first constructor of \texttt{R2} describes the case where the chopped head is exactly at height $2$. The others constructors allow us to consider beheadings at height strictly greater than $2$.

@@

 We define an addition in type \texttt{E0}, using the function{T1.plus}
and its properties.

\begin{Coqsrc}
Search   (nf (_ + _)%t1).
\end{Coqsrc}

\begin{Coqanswer}
plus_nf: forall a : T1, nf a -> forall b : T1, nf b -> nf (a + b)
\end{Coqanswer}

>>>>

In order to describe trees where each node can have an arbitrary (but finite) number of sons, it is usual to define a type where each node carries a \emph{forest}, \emph{i.e} a list of trees
(see for instance Chapter 14, pages 400-406 of \cite{BC04}).

@@

\vspace{4pt}
\noindent
\emph{From Module~\href{../theories/html/hydras.Hydra.Hydra_Definitions.html\#Hydra}{Hydra.Hydra\_Definitions}}

@@

\vspace{4pt}
\noindent
\emph{From Module~\href{../theories/html/hydras.Hydra.Hydra_Definitions.html\#head}{Hydra.Hydra\_Definitions}}

@@

\vspace{4mm}
\noindent
\emph{From Module~\href{../theories/html/hydras.Hydra.Hydra_Examples.html\#Hy}{Hydra.Hydra\_Examples}}

@@

\vspace{4pt}
\noindent
\emph{From Module~\href{../theories/html/hydras.Hydra.Hydra_Definitions.html\#hcons_mult}{Hydra.Hydra\_Definitions}}

@@

(** A node with n clones of the same daughter *)

@@

@@

In order to  define a recursive function over the type \texttt{Hydra}, one has to consider the three constructors 
\texttt{node}, \texttt{hnil} and \texttt{hcons} of the mutually inductive types \texttt{Hydra} and \texttt{Hydrae}. 
Let us define for instance the function which  computes the number of nodes of any hydra:

@@

Let us now use \texttt{Hydra\_rect2} for proving that the height of any hydra is strictly less than its size.
Using this scheme requires an auxiliary predicate, called \texttt{P0} in \texttt{Hydra\_rect2}'s statement.

@@

The rest of the definition is composed of two mutually inductive relations on hydras and sequences of hydras. The first constructor of \texttt{R2} describes the case where the chopped head is exactly at height $2$. The others constructors allow us to consider beheadings at height strictly greater than $2$.

@@

 We define an addition in type \texttt{E0}, since the sum of two terms in normal form is in normal form too.
